The \dealii{} Library, Version 8.4.0

### 2016-02-24 deal84.tex
update title
remove preliminary multigrid entries
as discussed with Guido and Martin
minor edits

\title{The \dealii{} Library, Version 8.4}
\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Texas A\&M University, College Station,
    TX 77843, USA,
    {\texttt{bangerth@math.tamu.edu}}}
\author[2]{Denis Davydov}
\affil[2]{???,
  {\texttt{???}}}
\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}
\author[4]{Luca Heltai}
\affil[4]{SISSA - International School for Advanced Studies, Via
  Bonomea 265, 34136 Trieste, Italy,
  {\texttt{luca.heltai@sissa.it}}}
\author[5]{Guido Kanschat}
\affil[5]{Interdisciplinary Center for Scientific Computing (IWR),
  Universit{\"a}t Heidelberg, Im Neuenheimer Feld 368, 69120 Heidelberg, Germany,
  {\texttt{kanschat@uni-heidelberg.de}}}
\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics, Technische
  Universit{\"a}t M{\"u}nchen, Boltzmannstr.~15, 85748 Garching b. Mænchen,
  Germany,
  {\texttt{kronbichler@lnm.mw.tum.de}}}
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics, University of Minnesota, 127 Vincent Hall,
  206 Church Street SE, Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}
\author[8]{Bruno Turcksin}
\affil[8]{Department of Mathematics, Texas A\&M University, College Station,
  TX 77843, USA,
  {\texttt{turcksin@math.tamu.edu}}}
\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}
%\author[8]{Toby~D.~Young}
%\affil[8]{Institute of Fundamental Technological Research of the Polish
%  Academy of Sciences, ul. Pawi{\'n}skiego 5b, Warsaw 02-106, Poland,
%  {\texttt{tyoung@ippt.pan.pl}}}

@@

The major changes of this release are:
\begin{itemize}
\item Preliminary support for parallel, adaptive, geometric multigrid
\item Parallel triangulations can now be partitioned in ways that allow
  weighting cells differently
\item Improved support for mixed-type arithmetic throughout the library
\item A new triangulation type that supports parallel computations
  but ensures that the entire mesh is available on every processor
\item An implementation of the Rannacher-Turek element, as well as an
  element that extends the usual Q(p) elements by bubble functions
\item Second and third derivatives of finite element fields are now
  computed exactly.
\item The various \emph{Concepts}, or requirements on template parameters
  in the library, are now consistently labeled and documented as such.
\item The interface between finite elements, quadrature, mapping, and the
  FEValues class has been rewritten. It is now much better documented
\item  More than 140 other features and bugfixes.
\end{itemize}
Some of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

\subsection{Preliminary support for parallel, adaptive, geometric
  multigrid}

\marginpar{Martin/Timo -- can you write this section?}
...

@@

When evaluating finite element fields or their derivatives at
a points $\mathbf x_q$, one typically has to do an operation of the form
\begin{align*}
  u_h(\mathbf x_q) &= \sum_{j} U_j \varphi_j(\mathbf x_q),
  \\
  \nabla u_h(\mathbf x_q) &= \sum_{j} U_j \nabla\varphi_j(\mathbf x_q).
\end{align*}
The value or derivatives of shape functions, $\varphi_j(\mathbf x_q)$
or $\nabla\varphi_j(\mathbf x_q)$ are internally evaluated by classes
derived from the \texttt{FiniteElement} and \texttt{Mapping}, and are
computed as scalars or tensors of type \texttt{double}. On the other
hand, the expansion coefficients of the field, $U_j$ are stored in
vectors of types chosen by the user; their underlying representation
can be \texttt{double}, but also \texttt{float}, \texttt{long double},
\texttt{PetscScalar}, or \texttt{std::complex<float>}. It could also
be an autodifferentiation type.

@@

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award
No. EAR-0949446 and The University of California -- Davis.

>>>>

\title{The \dealii{} Library, Version 8.4.0}
\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Texas A\&M University, College Station,
    TX 77843, USA,
    {\texttt{bangerth@math.tamu.edu}}}
\author[2]{Denis Davydov}
\affil[2]{???,
  {\texttt{???}}}
\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}
\author[4]{Luca Heltai}
\affil[4]{SISSA - International School for Advanced Studies, Via
  Bonomea 265, 34136 Trieste, Italy,
  {\texttt{luca.heltai@sissa.it}}}
\author[5]{Guido Kanschat}
\affil[5]{Interdisciplinary Center for Scientific Computing (IWR),
  Universit{\"a}t Heidelberg, Im Neuenheimer Feld 368, 69120 Heidelberg, Germany,
  {\texttt{kanschat@uni-heidelberg.de}}}
\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics, Technische
  Universit{\"a}t M{\"u}nchen, Boltzmannstr.~15, 85748 Garching b. Mænchen,
  Germany,
  {\texttt{kronbichler@lnm.mw.tum.de}}}
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics, University of Minnesota, 127 Vincent Hall,
  206 Church Street SE, Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}
\author[8]{Bruno Turcksin}
\affil[8]{Department of Mathematics, Texas A\&M University, College Station,
  TX 77843, USA,
  {\texttt{turcksin@math.tamu.edu}}}
\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}
%\author[8]{Toby~D.~Young}
%\affil[8]{Institute of Fundamental Technological Research of the Polish
%  Academy of Sciences, ul. Pawi{\'n}skiego 5b, Warsaw 02-106, Poland,
%  {\texttt{tyoung@ippt.pan.pl}}}

@@

The major changes of this release are:
\begin{itemize}
\item Parallel triangulations can now be partitioned in ways that allow
  weighting cells differently
\item Improved support for mixed-type arithmetic throughout the library
\item A new triangulation type that supports parallel computations
  but ensures that the entire mesh is available on every processor
\item An implementation of the Rannacher-Turek element, as well as an
  element that extends the usual Q(p) elements by bubble functions
\item Second and third derivatives of finite element fields are now
  computed exactly.
\item The various \emph{Concepts}, or requirements on template parameters
  in the library, are now consistently labeled and documented as such.
\item The interface between finite elements, quadrature, mapping, and the
  FEValues class has been rewritten. It is now much better documented
\item  More than 140 other features and bugfixes.
\end{itemize}
Some of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

@@

When evaluating finite element fields or their derivatives at
a points $\mathbf x_q$, one typically has to do an operation of the form
\begin{align*}
  u_h(\mathbf x_q) &= \sum_{j} U_j \varphi_j(\mathbf x_q),
  \\
  \nabla u_h(\mathbf x_q) &= \sum_{j} U_j \nabla\varphi_j(\mathbf x_q).
\end{align*}
The value or derivatives of shape functions, $\varphi_j(\mathbf x_q)$
or $\nabla\varphi_j(\mathbf x_q)$ are internally evaluated by classes
derived from the \texttt{FiniteElement} and \texttt{Mapping}, and are
computed as scalars or tensors of type \texttt{double}. On the other
hand, the expansion coefficients of the field, $U_j$ are stored in
vectors of types chosen by the user; their underlying representation
can be \texttt{double}, but also \texttt{float}, \texttt{long double},
\texttt{PetscScalar}, or \texttt{std::complex<float>} for example. It could also
be an autodifferentiation type.

@@

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award No. EAR-0949446 and The University of California—Davis, and National Science Foundation grant DMS1522191.
